Background Subtraction based on Deep Feature Transformation Learning Background Subtraction

### 2018-03-10 draft.tex
introduction 修改

\begin{abstract}
% 背景建模是一个复杂的问题
Background subtraction is a fundamental problem of computer vision.
% 为什么复杂
The main challenges of background subtraction comes from the diversity and the complexity of natural scenes.
% 以前的工作是怎么做的
Plenty of previous works are proposed to handle this problem by artificial model.
% 我们是怎么做的
%Previous works in this field were proposed by designing an artificial model, 
In this paper,
we propose a self-adaption solution with the utilization of convolutional neural networks, 
and a novel background subtraction model named Deep Feature Transformation Learning is proposed.
% 动机是什么
With the motivation of finding a new representation of pixels’ historical observations in a new feature space.
% 怎么做的 XXX 这两句话介绍方法，但我实在是看不懂，你再改改
The videos are divided into fixed length image blocks, which are later transformed into the pixel’s observation patches as the input of a FCN for learning the variation of pixels.
We conduct our training and prediction processes on block level.
The architecture of the FCN is devised from the semantic segmentation problem.
% 效果好
Comparisons with several state-of-the-art algorithms in well-known benchmark show the superiority of proposed approach.
\end{abstract}

@@

% 说明问题的本质是什么

% 以这个本质为基础来评价现存方法

% 现存方法失败的原因是什么

% 我们的方法针对这个原因怎么样了

% XXX 为什么效果会好，同时也是我们方法的创新点, 最重要的还要结合图来说，

% 总结方法的思路

% 第三段介绍具体是怎么做的
% 首先一句到两句，最多３句话总结你的方法的过程

% 补充方法的细节

% 这些细节带来的好处

% 最后整个ｌｉｓｔ把方法的contribution 列出来
The contribution of proposed approach are summarized as follows:
\begin{itemize}
    \item We proposed the Deep Feature Transformation Learning model for background subtraction in complexly natural scenes.
        % 以前怎么做的
        Unlike previous XXX
        % 我们这么做有什么好处

        % 为什么要reshape 
    \item The observations in a particular pixel are reshaped into block 
        % 这么做额目的是什么，好处什么
\end{itemize}

In order to present a better and universal solution, we proposed the Deep Pixels’ Variation Learning (DPVL) model for Background Subtraction in diversely natural scenes.
In our method, the main job is to transform the sequence of pixels into another sequence which is easy for classification.
%XXX introduction 里最好不要出现公式
\begin{equation}
    sq_1 = \{p_1,p_2,\cdots, p_n\} -> sq_2 = \{f_1, f_2, \cdots, f_n\}
\end{equation}
For $sq_1$, it is a sequence of pixels' intensity, which is hard to classify which entry is foreground or background.
%
But in $sq_2$, it is more easy to classified, since the output of

In this paper, pixel’s observation patches are proposed to describe the historical observation of pixels.
And a random initialized FCN network is trained to learn the historical observation of pixels and generate a new representation in a new feature space.
We take advantage of the strong learning ability of FCN to learn a new representation of the Pixel’s observation patches in a new space where the pixels can be easily classified to background and foreground.

>>>>

\begin{abstract}
% 背景建模是一个复杂的问题
Background subtraction is a fundamental problem of computer vision.
% 为什么复杂
The main challenges of background subtraction comes from the diversity and the complexity of natural scenes.
% 以前的工作是怎么做的
Plenty of previous works are proposed to handle this problem by artificial model.
% 我们是怎么做的
%Previous works in this field were proposed by designing an artificial model, 
In this paper,
we propose a self-adaption solution with the utilization of convolutional neural networks, 
and a novel background subtraction model named Deep Feature Transformation Learning is proposed.
% 动机是什么
With the motivation of finding a new representation of pixels’ historical observations in a new feature space.
% 怎么做的 XXX 这两句话介绍方法，但我实在是看不懂，你再改改
% We conduct our training and prediction processes on block level.
The videos are divided into image blocks, which are later transformed into the pixel’s observation patches.
Moreover, these patches are taken as the input of a Fully Convolutional Network(FCN). 
With the strong learning ability of FCN, we can finally get a new representation from raw RGB data, which is easier for the classification.

The architecture of the FCN proposed in this paper is devised from the semantic segmentation problem.
% 效果好
Comparisons with several state-of-the-art algorithms in well-known benchmark show the superiority of proposed approach.
\end{abstract}

@@

% 说明问题的本质是什么 
Typically, Background subtraction can be viewed as a binary classification, where pixels in video stream are divided into two
types, either foreground or background.

% 以这个本质为基础来评价现存方法
With a huge number of works, existed algorithms have already achieved well performances in the scenes of low diversity or complexity,
such as the indoor scenes. However, those performance on real-world scenes like dynamic background, bad weather, illumination changes,
intermittent object motion are still not satisffied.

% 现存方法失败的原因是什么
This is principally because the major methods, in most cases, try to find a universal solution by generating some universal 
background models for later linear classification; for instance, the earlier Frame Difference Methods, trying to get a fixed 
image as background to classify each pixels. The fundamental problem lies in that linear classifier might not be powerful enough for the job,
due to the complexity and the diversity of natural scenes.

%我们的方法针对这个原因怎么样了
In order to present a better and universal solution, we proposed the Deep Feature Transformation Learning model for Background Subtraction 
in complexly natural scenes.

% XXX 为什么效果会好，同时也是我们方法的创新点, 最重要的还要结合图来说，
With the strong learning ability of FCN, we can easily get a new representation of pixels' historical observations which are much easier and clearer to distinguish.

% 总结方法的思路
In our method, the main job is to transform the sequence of pixels into another sequence which is easy for classification.

sq1 = {p_1,p_2,...p_n} -> sq2 = {f_1,f_2,...f_n}                     (1)

For sq1, it is a sequence of pixels' intensity, which is hard to classify which entry is foreground or background.
But in sq2, it is more easy to classified, since the output of the network is the label of each entry in sequence.

% 第三段介绍具体是怎么做的
More particularly, videos are divided into image blocks at the beginning. Then, pixel's observation patches are extracted from these blocks and sent to a FCN.
The FCN will learn and transform these patches into prediction patches where pixels are clearly for classification.
% 首先一句到两句，最多３句话总结你的方法的过程

% 补充方法的细节
In this paper, pixel’s observation patches are proposed to describe the historical observation of pixels and also as the input of our network. 
A random initialized FCN network is trained to learn the historical observation of pixels and generate a new representation in a new feature space.

% 这些细节带来的好处
We take advantage of the strong learning ability of FCN to learn a new representation of the Pixel’s observation patches in a new space where 
the pixels can be easily classified to background and foreground.

% 最后整个ｌｉｓｔ把方法的contribution 列出来
The contribution of proposed approach are summarized as follows:
(1) We present the Pixel's observation patches which give us the ability to process the pixel's historical observation with a FCN.
(2) We present a novel FCN architecture for Background Subtraction.

\begin{itemize}
    \item    
        % 以前怎么做的
        Most existed methods are based on Background models. 
        Unlike previous Background model based algorithms, we focus on the pixels stream itself, trying to find a space where the new representation
        of pixels are easier to distinguish. 
        % 我们这么做有什么好处
        The reason why we choose this way for the job is because we can't find a perfect background model which can adapt to all kinds of nature 
        scenes and various tasks. In this condition, we avoid to build a universal background model. And the experiment shows a good performance 
        compared with some state-of-art methods.

        % 为什么要reshape 
    \item The observations in a particular pixel are reshaped into blocks, that's because our network needs fixed size input, we also tried different 
        size of input.
        % 这么做额目的是什么，好处什么
\end{itemize}
%XXX introduction 里最好不要出现公式
\begin{equation}
    sq_1 = \{p_1,p_2,\cdots, p_n\} -> sq_2 = \{f_1, f_2, \cdots, f_n\}
\end{equation}
For $sq_1$, it is a sequence of pixels' intensity, which is hard to classify which entry is foreground or background.
%
But in $sq_2$, it is more easy to classified, since the output of the network is the label of each entry in sequence.
